---
title: "Launch a task in Python with Shinybach"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lancement_python}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = F}
require(shinybatch)
```

In its basic use, the package runs a R function by :  

- sourcing the R script of the function
- retrieving the function name and args in the yaml conf file
- calling the function by using *do.call()* 


To run a script that is not written in R, it is possible to use the R function as a wrapper.  

<br>

We give an example for ``Python``, using package **reticulate**. Another solution would be to use the *system()* function. 
This example re-uses the demo app (stored in the package: ``system.file( "demo_app.R", package = "shinybatch")``):  

<br>

First block (same as the demo app):  

- load packages
- create temporary directory to save the configuration files
- set the path of the R function
- initialize the scheduler  

```{r, eval = F}
require(shiny)
require(shinydashboard)
require(DT)
require(shinybatch)

# create directory for conf
dir_conf <- paste0(tempdir(), "/conf")
if (dir.exists(dir_conf)) unlink(dir_conf, recursive = TRUE)
dir.create(dir_conf, recursive = T)

# get path of the wrapper of th python fun
wrapper_path <- system.file("/ex_fun/sb_fun_demo_app_python.R", package = "shinybatch")

# init shceduler
dir_scheduler <- paste0(tempdir(), "/cron_demo_python")
if (dir.exists(dir_scheduler)) unlink(dir_scheduler, recursive = TRUE)
dir.create(dir_scheduler, recursive = T)

scheduler_add(dir_scheduler = dir_scheduler,
              dir_conf = dir_conf,
              max_runs = 1,
              head_rows = NULL,
              taskname = "cr_python_demo")
```


The wrapper function:  

- The Python function can be run as is
- the arguments should be provided in R and then cast to python in the wrapper or in the Python fun  

The Python function applies a single regexpr to change 'input' to 'output'.
```{r, eval = F}
wrapper_py <- function(vect) {
  require(reticulate)

  env <- py_run_file(system.file("/ex_fun/sb_fun_demo_app_python.py", package = "shinybatch")) ;
  env$apply_regexprs(vect = vect,
                     regexprs = reticulate::dict(list("input" = "output")))
}
```

<br>

Second block:  

- define the Shiny UI  

Modifications:  

- new inputs to fit the usecase  
```{r, eval = F}
# define UI
ui <- shinydashboard::dashboardPage(
  shinydashboard::dashboardHeader(title = "Shinybatch"),
  shinydashboard::dashboardSidebar(disable = T),
  shinydashboard::dashboardBody(
    fluidRow(
      shinydashboard::tabBox(width = 12,
                             tabPanel("Configure tasks",
                                      fluidRow(
                                        # conf args
                                        column(2,
                                               numericInput("priority", "Priority",
                                                            min = 0, max = 10, value = 1, step = 1)
                                        ),
                                        column(2,
                                               textInput("title", "Title", 
                                                         value = "Task title", width = "100%")
                                        ),
                                        column(3,
                                               textInput("description", "Description", 
                                                         value = "Task description", width = "100%")
                                        ),
                                        # fun args
                                        column(3,
                                               textInput("regexpr", "Regular expression", 
                                                         value = "Test input", width = "100%")
                                        ),
                                        column(2,
                                               numericInput("sleep_time", "Sleep time (s)",
                                                            min = 0, max = 30, value = 0, step = 1)
                                        )
                                      ),
                                      hr(),
                                      fluidRow(
                                        column(6, offset = 3,
                                               actionButton("go_task", "Configure the task", width = "100%")
                                        ) 
                                      )
                                      
                             ),
                             tabPanel("View tasks",
                                      fluidRow(
                                        column(12,
                                               tasks_overview_UI("my_id_2")
                                        )
                                      ),
                                      conditionalPanel(condition = "output.launch_task",
                                                       br(),
                                                       hr(),
                                                       fluidRow(
                                                         conditionalPanel(condition = "output.launch_task",
                                                                          column(12,
                                                                                 div(actionButton("show_task", "Display task result", width = "40%"),
                                                                                     align = "center")
                                                                          ) 
                                                         ),
                                                         column(12,
                                                                conditionalPanel(condition = "input.show_task > 0",
                                                                                 textOutput("task_text")                                 
                                                                )
                                                         )
                                                       )
                                      )
                             )
      )               
    )
  )
)
```

<br>

Third block:  

- define the Shiny server  
  
Modifications:  

- ajust *callModule()* to fit the usecase  
```{r, eval = F}
# define server 
# call both shinybatch modules + display result
server <- function(input, output, session) {
  
  # call module to configure a task
  # connect app inputs to the module
  callModule(configure_task_server, "my_id_1",
             btn = reactive(input$go_task),
             dir_path = dir_conf,
             conf_descr = reactive(list("title" = input$title,
                                        "description" = input$description)),
             fun_path = wrapper_path,
             fun_name = "wrapper_py",
             fun_args = reactive(list(vect = input$regexpr)),
             priority = reactive(input$priority))
  
  # call module to view tasks
  sel_task <- callModule(tasks_overview_server, "my_id_2",
                         dir_path = dir_conf,
                         update_mode = "reactive",
                         allowed_status = c("waiting", "running", "finished", "error"),
                         allowed_run_info_cols = NULL,
                         allowed_function_cols = NULL,
                         allow_descr = T,
                         allow_args = T)
  
  # check if sel_task can be displayed
  output$launch_task <- reactive({
    ! is.null(sel_task()) && length(sel_task()) > 0 && sel_task()$status == "finished"
  })
  outputOptions(output, "launch_task", suspendWhenHidden = FALSE)
  
  # display task
  output$task_text <- renderText({
    cpt <- input$show_task
    sel_task <- sel_task()
    
    isolate({
      if (cpt > 0 && length(sel_task) > 0 && sel_task$status == "finished") {
        readRDS(paste0(sel_task$path, "/res.RDS"))
      }
    })
  })
}
```

<br>

Launch the app:  
```{r, eval = F}
# launch app
shiny::shinyApp(ui = ui,
                server = server,
                onStart = function() {
                  onStop(function() {
                    scheduler_remove(taskname = "cr_python_demo")
                  })
                })
```